Language-Based Security for Low-Level MPC

### 2024-06-29 ppdp24/response.txt

Many thanks to the reviewers for their thoughtful comments. To be succinct we restrict our responses to main issues raised.

Reviewer 1 comments:

"The definition of sigma \cap sigma' does not line up with its usage in many places. The intersection is defined so that the domain of the intersection is the intersection of the domains. This is corroborated by the claim that sigma \sub sigma' iff (sigma \cap sigma') = sigma...However, in numerous locations (sigma \cap sigma') seems to be used in place of the union (sigma \cup sigma') which would be correct. Here, one would define (sigma \cup sigma')(x) to be sigma(x) if x \in dom(\sigma) and sigma'(x) if x \in dom(\sigma') with the condition that they agree on their intersection (with the union being undefined otherwise). Note that this satisfies sigma \sub sigma' iff (sigma \cup sigma') = sigma'."

Our definition of sigma \cap sigma' is in fact the one that the reviewer identifies as correct, not the incorrect one the reviewer suggests. In Section 2.2 we say "we write sigma \cap sigma to denote the combination of sigma and sigma' assuming sigma(x) = sigma'(x) for all x in dom(sigma) \cap dom(sigma'), otherwise sigma cap sigma' is undefined." Perhaps the word "combination" here was misleading but we meant "unioning" in the sense the reviewer means. It is also possible that the use of \cap instead of another symbol is confusing, and we can certainly clarify this in a revision and/or use a different symbol. However the reviewer's definition is the one intended in our text.

"Def. 3.3 also has typing problems. In the numerator, P_X specifically has domain mems(X), but its argument (sigma \cap sigma') is in mems(Y) with Y \sub X. I believe the definition would be correct if the union is used instead."

Our previous comment (about sigma \cap sigma') applies to this also.

"The text in Section 3.1 is confusing at best, and I believe actually incorrect (in part due to the intersection/union confusion). First, for a PMF P, P should be viewed as a function mems(X) -> R for some parameter X. This is implicit in Def. 3.1, but making it explicit would help elucidate the issues with definitions 3.2 and 3.3."

Our previous comment applies to this in part, especially wrt correctness. Additionally, in Definition 3.3 we introduce syntactic sugaring P(sigma) to denotes P_X(sigma) where dom(X) is given (as X), which we believe is conventional. However we agree with the reviewer that subsequent definitions would be clarified by being explicit (about X) in Definitions 3.1-3.

"In Def. 3.2, the implied domain of P is mems(Y) for some X \sub Y. The marginal should be a restriction to a smaller/shorter memory. Then sigma' is given as being in mems(X - dom(dom(P))). It's not clear what dom(dom(P)) means. If dom(P) = mems(Y) and dom(mems(Y)) = Y, then it might mean Y. But then X - Y is empty since X \sub Y. Probably the proper definition should be..."

Yes we meant "mems(dom(dom(P)) - X)" (not "mems(X - dom(dom(P)))"), with that edit the definition comports with the one the reviewer suggests. The meaning of dom(dom(P)) is determined by the definition of memories in Section 2.2 and Definition 3.1 (though we can clarify this in the definition).

"Fig. 2, middle: Are the outer brackets on lines 2-4 needed? In any case, their meaning is never defined (though one can infer it)."

The meaning of the outer brackets is defined in Section 2.2 in the paragraph just before Section 2.3.

"One technical error is in Secton 2.3. The subtractions are all backwards."

Yes this was a typo, we did have the order right in Section 2.1.

"Ultimately, these technical issues make it exceedingly difficult to judge the coreectness."

Overall, it seems that a misunderstanding of our definition of sigma \cap \sigma' led to an impression of more general incorrectness. We hope that our above comments have clarified that our definition aligns with the one the reviewer states to be correct, since further we believe that the Definitions in Section 3.1 are more or less standard modulo some specialized notation. We can certainly clarify and improve this notation, e.g., by using a different symbol for \cap and highlighting our Definition.

Reviewer 2 comments:

"- Page 8, Section 6. Why do you call Prelude a "metalanguage"? A metalanguage is a language for defining languages (example: BNF-like formats such as yacc or bison). In fact, Prelude is a language which can be translated into Overture programs, and the "semantics" defined in Figure 5 is the translation from Prelude to Overture. Indeed, Prelude has no real operational semantics acting on a memory; only Overture has it."

Our use of the term "metalanguage" was based on previous "staged" or "metaprogramming" languages such as MetaML, where programs produce programs. The semantics of Prelude (Figure 5) specify that Prelude programs yield Overture programs as side effects of computation, hence our use of the term. We now recognize that the reviewer's definition is popular so we can change "metalanguage" to "staged language" to avoid misleading readers.

### 2024-06-29 ppdp24/response.txt

Many thanks to the reviewers for their thoughtful comments. We will consider and address all of them in future iterations of this work. To be succinct we restrict our responses to main issues raised.

@@

The meaning of the outer brackets is defined in Section 2.2 in the paragraph just before Section 2.3.

"One technical error is in Secton 2.3. The subtractions are all backwards."

Yes this was a typo, we did have the order right in Section 2.1.

"Ultimately, these technical issues make it exceedingly difficult to judge the coreectness..."

Overall, it seems that a misunderstanding of our definition of sigma \cap \sigma' led to an impression of more general incorrectness. We hope that our above comments have clarified that our definition aligns with the one the reviewer states to be correct, since further we believe that the Definitions in Section 3.1 are more or less standard modulo some specialized notation. We can certainly clarify and improve this notation , e.g., by using a different symbol for \cap and highlighting our Definition.

### 2024-07-15 ppdp24/example-bdoz.tex
checkpoint

A field value $v$ is secret shared among 2 clients in BDOZ in the same
manner as in GMW.  Each client $\cid$ gets a pair of the form
$(v_\cid,m_\cid)$, where $v_\cid$ is a share of $v$ reconstructed by
addition, i.e., $v = \fcod{v_1 \fplus v_2}$, and $m_\cid$ is a MAC of
$v_\cid$.  More precisely, $m_\cid = k + (k_\Delta * v_\cid)$ where
\emph{keys} $k$ and $k_\Delta$ are known only to $\cid' \ne \cid$ and
$k_\Delta$. The \emph{local key} $k$ is unique per MAC, while the
\emph{global key} $k_\Delta$ is common to all MACs authenticated by
$\cid'$. This is a semi-homomorphic encryption scheme that supports
addition of shares and multiplication of shares by a constant-- for
more details the reader is referred to Orsini
\cite{10.1007/978-3-030-68869-1_3}. We note that while we restrict
values $v$, $m$, and $k$ to the same field in this presentation for
simplicity, in general $m$ and $k$ can be in extensions of
$\mathbb{Z}_p$.

>>>>

A field value $v$ is secret shared among 2 clients in BDOZ in the same
manner as in GMW.  Each client $\cid$ gets a pair of the form
$(v_\cid,m_\cid)$, where $v_\cid$ is a share of $v$ reconstructed by
addition, i.e., $v = \fcod{v_1 \fplus v_2}$, and $m_\cid$ is a MAC of
$v_\cid$.  More precisely, $m_\cid = k + (k_\Delta * v_\cid)$ where
\emph{keys} $k$ and $k_\Delta$ are known only to $\cid' \ne \cid$ and
$k_\Delta$. The \emph{local key} $k$ is unique per MAC, while the
\emph{global key} $k_\Delta$ is common to all MACs authenticated by
$\cid'$. This is a semi-homomorphic encryption scheme that supports
addition of shares and multiplication of shares by a constant-- for
more details the reader is referred to Orsini
\cite{10.1007/978-3-030-68869-1_3}. We note that while we restrict
values $v$, $m$, and $k$ to the same field in this presentation for
simplicity, in general $m$ and $k$ can be in extensions of
$\mathbb{F}_p$.

### 2024-07-15 ppdp24/hyper.tex
checkpoint

\emph{Integrity} is an important hyperproperty in security models that admit
malicious adversaries. Consistent with formulations in deterministic settings,
we have already defined protocol confidentiality as the preservation of low equivalence
(of secrets and views), and now we define protocol integrity as the preservation
of high equivalence (of secrets and views). Intuitively, this property says
that any adversarial strategy either ``mimics'' a passive strategy with some
choice of inputs or causes an abort.
\begin{definition}[Integrity]
  \label{def-integrity}
  We say that a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ has
  \emph{integrity} iff for all $H$, $C$, and $\adversary$,
  if $\store \in \aruns(\prog)$ 
  then there exists $\store' \in \mems(S)$ with $\store_{S_H} = \store'_{S_H} $ and:
    $$
    \condd{\progtt(\prog,\adversary)}{X}{\store_{S_H \cup \cinputs}} =
    \condd{\progtt(\prog)}{X}{\store'}
    $$ 
  where $X \defeq (\houtputs \cup O_H) \cap \dom(\store)$. 
\end{definition}
A first important observation is that integrity preserves protocol correctness
for honest outputs, except for the possibility of abort. 
\begin{lemma}
  \label{lemma-malicious-correct}
  If a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ is passive correct for
  $\idealf$ and
  has integrity, then for all $H$, $C$, and $\adversary$ and $\store_1 \in \mems(S_H)$,
  there exists $\store_2 \in \mems(S_C)$ such that:
  $$
  \idealf(\store_1 \cap \store_2)_H \cup \{ \bot \} \supseteq
    \support(\progtt(\prog,\adversary)(O_H|\store_1))
  $$
\end{lemma}
The following result establishes that integrity implies malicious
security for protocols that are passive secure (which also subsumes
correctness). 
\begin{theorem}
  \label{theorem-integrity}
  If a protocol is passive secure and has integrity, then it
  is malicious secure.
\end{theorem}

>>>>

\emph{Integrity} is an important hyperproperty in security models that admit
malicious adversaries. Consistent with formulations in deterministic settings,
we have already defined protocol confidentiality as the preservation of low equivalence
(of secrets and views), and now we define protocol integrity as the preservation
of high equivalence (of secrets and views). Intuitively, this property says
that any adversarial strategy either ``mimics'' a passive strategy with some
choice of inputs or causes an abort.
\begin{definition}[Integrity]
  \label{def-integrity}
  We say that a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ has
  \emph{integrity} iff for all $H$, $C$, and $\adversary$,
  if $\store \in \aruns(\prog)$ 
  then there exists $\store' \in \mems(S)$ with $\store_{S_H} = \store'_{S_H} $ and:
    $$
    \condd{\progtt(\prog,\adversary)}{X}{\store_{S_H \cup \cinputs}} =
    \condd{\progtt(\prog)}{X}{\store'}
    $$ 
  where $X \defeq (\houtputs \cup O_H) \cap \dom(\store)$. 
\end{definition}
A first important observation is that integrity preserves protocol correctness
for honest outputs, except for the possibility of abort. 
\begin{lemma}
  \label{lemma-malicious-correct}
  If a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ is passive correct for
  $\idealf$ and
  has integrity, then for all $H$, $C$, $\adversary$, $\store_1 \in \mems(S_H)$,
  $\ox{\cid} \in (O_H)$, and $\mv \in \mathbb{F}_p$, if:
  $$
  \progtt(\prog,\adversary)(\{ \ox{\cid} \mapsto \mv \} \mid \store_1) > 0
  $$
  then exists $\store_2 \in \mems(S_C)$ such that:
  $$
  \idealf(\store_1 \uplus \store_2)(\ox{\cid}) = \mv
  $$
\end{lemma}
The following result establishes that integrity implies malicious
security for protocols that are passive secure (which also subsumes
correctness). 
\begin{theorem}
  \label{theorem-integrity}
  If a protocol is passive secure and has integrity, then it
  is malicious secure.
\end{theorem}

### 2024-07-15 ppdp24/lang.tex
checkpoint

The syntax of $\minifed$, defined in
Figure \ref{fig-minifed}, includes values $v$ and standard
operations of addition, subtraction, and multiplication in
a finite field $\mathbb{F}_p$ where $p$ is some prime. 
Protocols are given input secret values $\secret{w}$
as well as random samples $\flip{w}$ on the input
tape, both of which are distinguished by
strings $w$. Protocols are sequences of assignment
commands of three different forms:
\begin{itemize}
\item $\eassign{\mesg{w}}{\cid_2}{\be}{\cid_1}$: This
  is a \emph{message send} where expression $\be$ is computed
  by client $\cid_1$ and sent to client $\cid_2$ as message
  $\mesg{w}$.
\item $\reveal{w}{\be}{\cid}$: This
  is a \emph{public reveal} where expression $\be$ is computed
  by client $\cid$ and broadcast to the federation, typically
  to communicate intermediate results for use in final output
  computations.
\item $\pubout{\cid}{\be}{\cid}$: This
  is an \emph{output} where expression $\be$ is computed
  by client $\cid$ and reported as its output.
\end{itemize}

Both messages $\mesg{w}$ and reveals $\rvl{w}$ can be
referenced in expressions, once they've been assigned.
This distinction between messages and broadcast public
reveal is consistent with previous formulations, e.g.,
\cite{6266151}.

We let $x$ range over \emph{variables} which are identifiers where
client ownership is specified- e.g.,
$\elab{\mesg{\mathit{foo}}}{\cid}$ is a message $\mathit{foo}$ that
was sent to $\cid$. We let $X$ range over sets of variables, and more
specifically, $S$ ranges over sets of secret variables
$\elab{\secret{w}}{\cid}$, $R$ ranges over sets of random variables
$\elab{\flip{w}}{\cid}$, $M$ ranges over sets of message variables
$\elab{\mesg{w}}{\cid}$, $P$ ranges over sets of public variables
$\rvl{w}$, and $O$ ranges over sets of output variables $\out{\cid}$.
Given a program $\prog$, we write $\iov(\prog)$ to denote the set $S
\cup M \cup P \cup O$ of variables in $\prog$ with ownership made
explicit and $\secrets(\prog)$ to denote $S$, and we write
$\flips(\prog)$ to denote the set $R$ of random samplings in $\prog$
with ownership made explicit. We write $\vars(\prog)$ to denote
$\iov(\prog) \cup \flips(\prog)$. For any set of variables $X$ and
parties $P$, we write $X_P$ to denote the subset of $X$ owned by any
party in $P$, in particular we write $X_H$ and $X_C$ to denote the
subsets belonging to honest and corrupt parties, respectively.

\subsection{Semantics}

\emph{Memories} are fundamental to the semantics of $\fedcat$ and
provide random tape and secret inputs to protocols, and also record
message sends, public broadcast, and client outputs. Memories $\store$ are finite
(partial) mapping from variables $x$ to values $v \in \mathbb{Z}_p$. The \emph{domain} of a
memory is written $\dom(\store)$ and is the finite set of variables on
which the memory is defined. We write $\store\{ x \mapsto v\}$ for
$x\not\in\dom(\store)$ to denote the memory $\store'$ such that
$\store'(x) = v$ and otherwise $\store'(y) = \store(y)$ for all $y
\in \dom(\store)$. We write $\store \subseteq \store'$ iff
$\dom(\store) \subseteq \dom(\store')$ and $\store(x) =
\store'(x)$ for all $x \in \dom(\store)$. We write $\store \cap
\store'$ to denote the combination of $\store$ and $\store'$
assuming $\store(x) = \store'(x)$ for all $x \in \dom(\store)
\cap \dom(\store')$, otherwise $\store \cap \store'$ is undefined.
We write $\store \subseteq \store'$ iff $\store \cap \store'
= \store$.

@@

Given a variable-free expression $\be$, we write $\cod{\be}$ to denote
the standard interpretation of $\be$ in the arithmetic field
$\mathbb{Z}_{p}$. With the introduction of variables to expressions,
we need to interpret variables with respect to a specific memory, and
all variables used in an expression must belong to a specified client.
Thus, we denote interpretation of expressions $\be$ computed on a
client $\cid$ as $\lcod{\store,\be}{\cid}$. This interpretation is
defined in Figure \ref{fig-minifed}. It is also parameterized by
$\delta$ which defines the semantics of library functions $f$.

The small-step reduction relation $\redx$ is then defined in Figure
\ref{fig-minifed} to evaluate commands. Reduction is a relation on
\emph{configurations} $(\store, \prog)$ where all three command forms-
message send, broadcast, and output- are implemented as updates to the
memory $\store$. We write $\redxs$ to denote the reflexive, transitive
closure of\ $\redx$.

\subsection{Example: Passive Secure Addition}

Shamir addition leverages homomorphic properties of addition in
arithmetic fields to implement secret addition. If a field value $v_1$
is in a uniform random distribution with other variables in a program,
then either  $v_1 \fplus v_2$ or $v_1 \fminus v_2$  is an encryption of $v_2$
where $v_1$ is an information theoretically secure one-time-pad, which
is exploited for secret sharing. Of course, $\fplus$ and $\fminus$ are also
meaningful operations over any two field values regardless of their distributions.

To sum their secret values $\secret{\cid}$, each client $\cid$ in
the federation $\{ 1, 2, 3 \}$  samples a value $\locflip$
that can be used as a one-time pad with another
random sample $\flip{x}$ and $\secret{\cid}$. This yields
two secret shares communicated as messages to the other clients,
while each client keeps $\locflip$ as its own share.
$$
\begin{array}{lll}
  \elab{\mesg{s1}}{2} &:=& \elab{(\locflip \fminus \flip{x} \fminus \secret{1})}{1} \\ 
  \elab{\mesg{s1}}{3} &:=& \elab{\flip{x}}{1} \\ 
  \elab{\mesg{s2}}{1} &:=& \elab{(\locflip \fminus \flip{x} \fminus \secret{2})}{2} \\ 
  \elab{\mesg{s2}}{3} &:=& \elab{\flip{x}}{2} \\ 
  \elab{\mesg{s3}}{1} &:=& \elab{(\locflip \fminus \flip{x} \fminus \secret{3})}{3} \\ 
  \elab{\mesg{s3}}{2} &:=& \elab{\flip{x}}{3}
\end{array}
$$
Due to field properties of $\fminus$ this scheme guarantees that messages
are viewed as random noise by any observer 
besides $\cid$ \cite{barthe2019probabilistic}. Next, each client
publicly reveals the sum of all of its shares, including its local
share. This step does reveal information about secrets-- note in
particular that $\locflip$ is reused and is no longer a one-time-pad:
$$
\begin{array}{lll}
  \rvl{1} &:=& \elab{(\locflip \fplus \mesg{s2} \fplus \mesg{s3})}{1} \\ 
  \rvl{2} &:=& \elab{(\mesg{s1} \fplus \locflip \fplus \mesg{s3})}{2} \\
  \rvl{3} &:=& \elab{(\mesg{s1} \fplus \mesg{s2} \fplus \locflip)}{3} 
\end{array}
$$
Finally, each client outputs the sum of each sum of shares, yielding
the sum of secrets. The protocol is correct because the outputs are all the
true sum of secrets, and it is secure because no more information about the
secrets other than that revealed by their sum is exposed.
$$
%\elab{\mesg{o1}}{2} &:=& \elab{(\locflip \fplus \mesg{s2} \fplus \mesg{s3})}{1} \\ 
  %\elab{\mesg{o1}}{3} &:=& \elab{(\locflip \fplus \mesg{s2} \fplus \mesg{s3})}{1} \\ 
  %\elab{\mesg{o2}}{1} &:=& \elab{(\mesg{s1} \fplus \locflip \fplus \mesg{s3})}{2} \\
  %\elab{\mesg{o2}}{3} &:=& \elab{(\mesg{s1} \fplus \locflip \fplus \mesg{s3})}{2} \\ 
  %\elab{\mesg{o3}}{1} &:=& \elab{(\mesg{s1} \fplus \mesg{s2} \fplus \locflip)}{3} \\ 
  %\elab{\mesg{o3}}{2} &:=& \elab{(\mesg{s1} \fplus \mesg{s2} \fplus \locflip)}{3}\\ 
  %\pubout{1} &:=& \elab{(\locflip \fplus \mesg{s2} \fplus \mesg{s3} + \mesg{o2} + \mesg{o3})}{1}
\begin{array}{lll}
  \out{1} &:=& \elab{(\rvl{1} \fplus \rvl{2} + \rvl{3})}{1}\\
  \out{2} &:=& \elab{(\rvl{1} \fplus \rvl{2} + \rvl{3})}{2}\\
  \out{3} &:=& \elab{(\rvl{1} \fplus \rvl{2} + \rvl{3})}{3}
\end{array}
$$

>>>>

The syntax of $\minifed$, defined in Figure \ref{fig-minifed},
includes values $v$ and standard operations of addition, subtraction,
and multiplication in a finite field $\mathbb{F}_p$ where $p$ is some
prime.  Protocols are given input secret values $\secret{w}$ as well
as random samples $\flip{w}$ on the input tape, implemented using a
\emph{memory} as described below (Section
\ref{section-lang-semantics}) where $w$ is a distinguishing 
identifier string. Protocols are sequences of assignment commands of three
different forms:
\begin{itemize}
\item $\eassign{\mesg{w}}{\cid_2}{\be}{\cid_1}$: This
  is a \emph{message send} where expression $\be$ is computed
  by client $\cid_1$ and sent to client $\cid_2$ as message
  $\mesg{w}$.
\item $\reveal{w}{\be}{\cid}$: This
  is a \emph{public reveal} where expression $\be$ is computed
  by client $\cid$ and broadcast to the federation, typically
  to communicate intermediate results for use in final output
  computations.
\item $\pubout{\cid}{\be}{\cid}$: This
  is an \emph{output} where expression $\be$ is computed
  by client $\cid$ and reported as its output. As a
  sanity condition we disallow commands
  $\pubout{\cid_1}{\be}{\cid_2}$ where $\cid_1\ne\cid_2$.
\end{itemize}
For example, in the following protocol, a client 1
subtracts a random sample $\flip{y}$ from $\mathbb{F}_p$ from their
secret value $\secret{x}$ and sends the result to client
2 as a message $\mesg{z}$:
$$
\eassign{\mesg{z}}{2}{(\secret{x} - \flip{y})}{1}
$$
Both messages $\mesg{w}$ and reveals $\rvl{w}$ can be
referenced in expressions once they've been defined.
This distinction between messages and broadcast public
reveal is consistent with previous formulations, e.g.,
\cite{6266151}.

We let $x$ range over \emph{variables} which are identifiers where
client ownership is specified- e.g.,
$\elab{\mesg{\mathit{foo}}}{\cid}$ is a message $\mathit{foo}$ that
was sent to $\cid$. We let $X$ range over sets of variables, and more
specifically, $S$ ranges over sets of secret variables
$\elab{\secret{w}}{\cid}$, $R$ ranges over sets of random variables
$\elab{\flip{w}}{\cid}$, $M$ ranges over sets of message variables
$\elab{\mesg{w}}{\cid}$, $P$ ranges over sets of public variables
$\rvl{w}$, and $O$ ranges over sets of output variables $\out{\cid}$.
Given a program $\prog$, we write $\iov(\prog)$ to denote the set $S
\cup M \cup P \cup O$ of variables in $\prog$ with ownership made
explicit and $\secrets(\prog)$ to denote $S$, and we write
$\flips(\prog)$ to denote the set $R$ of random samplings in $\prog$
with ownership made explicit. We write $\vars(\prog)$ to denote
$\iov(\prog) \cup \flips(\prog)$. For any set of variables $X$ and
clients $I$, we write $X_I$ to denote the subset of $X$ owned by any
client $\cid \in I$, in particular we write $X_H$ and $X_C$ to denote the
subsets belonging to honest and corrupt parties, respectively.

\subsection{Semantics}
\label{section-lang-semantics}

\emph{Memories} are fundamental to the semantics of $\fedcat$ and
provide random tape and secret inputs to protocols, and also record
message sends, public broadcast, and client outputs. Memories $\store$ are finite
(partial) mapping from variables $x$ to values $v \in \mathbb{F}_p$.
The \emph{domain} of a memory is written $\dom(\store)$ and is
the finite set of variables on which the memory is defined.
We write $\store\{ x \mapsto v\}$ for $x\not\in\dom(\store)$
to denote the memory $\store'$ such that
$\store'(x) = v$ and otherwise $\store'(y) = \store(y)$ for all $y
\in \dom(\store)$. We write $\store \subseteq \store'$ iff
$\dom(\store) \subseteq \dom(\store')$ and $\store(x) =
\store'(x)$ for all $x \in \dom(\store)$. We write $\store \uplus
\store'$ to denote the combination of $\store$ and $\store'$
assuming $\store(x) = \store'(x)$ for all $x \in \dom(\store)
\cap \dom(\store')$, otherwise $\store \uplus \store'$ is undefined.
\cnote{Check to make sure all $\cap$ and $\cup$s have been revised
with $\uplus$.}
We write $\store \subseteq \store'$ iff $\store \uplus \store'
= \store$.

@@

Given a variable-free expression $\be$, we write $\cod{\be}$ to denote
the standard interpretation of $\be$ in the arithmetic field
$\mathbb{F}_{p}$. With the introduction of variables to expressions,
we need to interpret variables with respect to a specific memory, and
all variables used in an expression must belong to a specified client.
Thus, we denote interpretation of expressions $\be$ computed on a
client $\cid$ as $\lcod{\store,\be}{\cid}$. This interpretation is
defined in Figure \ref{fig-minifed}. The small-step reduction relation
$\redx$ is then defined in Figure \ref{fig-minifed} to evaluate
commands. Reduction is a relation on \emph{configurations} $(\store,
\prog)$ where all three command forms- message send, broadcast, and
output- are implemented as updates to the memory $\store$. We write
$\redxs$ to denote the reflexive, transitive closure of\ $\redx$.

\subsection{Example: Passive Secure Addition}
\label{section-lang-example}

Shamir addition leverages homomorphic properties of addition in
arithmetic fields to implement secret addition. If a field value $v_1$
is uniformly random, then $v_1 \fminus v_2$ is an encryption of $v_2$
where $v_1$ is an information theoretically secure one-time-pad, which
is exploited for secret sharing, noting that $v_2$ can be
reconstructed by summing $v_1$ and $v_3 \defeq v_1 \fminus v_2$.

In $\minifed$, to privately sum secret values $\secret{\cid}$, each
client $\cid$ in the federation $\{ 1, 2, 3 \}$ samples a value
$\locflip$ that can be used as a one-time pad with another random
sample $\flip{x}$ and $\secret{\cid}$. This yields two secret shares
communicated as messages to the other clients, while each client keeps
$\locflip$ as its own share.
$$
\begin{array}{lll}
  \elab{\mesg{s1}}{2} &:=& \elab{(\secret{1} \fminus \locflip \fminus \flip{x})}{1} \\ 
  \elab{\mesg{s1}}{3} &:=& \elab{\flip{x}}{1} \\ 
  \elab{\mesg{s2}}{1} &:=& \elab{(\secret{2} \fminus \locflip \fminus \flip{x})}{2} \\ 
  \elab{\mesg{s2}}{3} &:=& \elab{\flip{x}}{2} \\ 
  \elab{\mesg{s3}}{1} &:=& \elab{(\secret{3} \fminus \locflip \fminus \flip{x})}{3} \\ 
  \elab{\mesg{s3}}{2} &:=& \elab{\flip{x}}{3}
\end{array}
$$
This scheme guarantees that messages
are viewed as random noise by any observer 
besides $\cid$ \cite{barthe2019probabilistic}. Next, each client
publicly reveals the sum of all of its shares, including its local
share. This step does reveal information about secrets-- note in
particular that $\locflip$ is reused and is no longer a one-time-pad:
$$
\begin{array}{lll}
  \rvl{1} &:=& \elab{(\locflip \fplus \mesg{s2} \fplus \mesg{s3})}{1} \\ 
  \rvl{2} &:=& \elab{(\mesg{s1} \fplus \locflip \fplus \mesg{s3})}{2} \\
  \rvl{3} &:=& \elab{(\mesg{s1} \fplus \mesg{s2} \fplus \locflip)}{3} 
\end{array}
$$
Finally, each client outputs the sum of each sum of shares, yielding
the sum of secrets. The protocol is correct because the outputs are all the
true sum of secrets, and it is secure because no more information about the
secrets other than that revealed by their sum is exposed.
$$
%\elab{\mesg{o1}}{2} &:=& \elab{(\locflip \fplus \mesg{s2} \fplus \mesg{s3})}{1} \\ 
  %\elab{\mesg{o1}}{3} &:=& \elab{(\locflip \fplus \mesg{s2} \fplus \mesg{s3})}{1} \\ 
  %\elab{\mesg{o2}}{1} &:=& \elab{(\mesg{s1} \fplus \locflip \fplus \mesg{s3})}{2} \\
  %\elab{\mesg{o2}}{3} &:=& \elab{(\mesg{s1} \fplus \locflip \fplus \mesg{s3})}{2} \\ 
  %\elab{\mesg{o3}}{1} &:=& \elab{(\mesg{s1} \fplus \mesg{s2} \fplus \locflip)}{3} \\ 
  %\elab{\mesg{o3}}{2} &:=& \elab{(\mesg{s1} \fplus \mesg{s2} \fplus \locflip)}{3}\\ 
  %\pubout{1} &:=& \elab{(\locflip \fplus \mesg{s2} \fplus \mesg{s3} + \mesg{o2} + \mesg{o3})}{1}
\begin{array}{lll}
  \out{1} &:=& \elab{(\rvl{1} \fplus \rvl{2} + \rvl{3})}{1}\\
  \out{2} &:=& \elab{(\rvl{1} \fplus \rvl{2} + \rvl{3})}{2}\\
  \out{3} &:=& \elab{(\rvl{1} \fplus \rvl{2} + \rvl{3})}{3}
\end{array}
$$
